Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-04-22 thirdPaper/draft/typeConeAssociahedra.tex
comments Lemma 4.47

\begin{lemma}\label{lemm::initial meshes}
Let~$\Lambda$ be an Artin algebra, and let~$P$ be an indecomposable projective~$\Lambda$-module.
%which is a brick.
% Let~$I$ be indecomposable injective with socle~$P/\operatorname{rad}P$, and~$\alpha$ be the composition~$P\to\operatorname{soc} I \to I$.
% Complete the morphism~$\alpha$ to a triangle~$P\to Y\to E\to \susp P$ in~$K^{[-1,0]}(\proj\Lambda)$, where~$Y$ is a minimal projective presentation of~$I$.
% Then~$Y\infl E\defl \susp P$ is an Auslander--Reiten conflation in~$K^{[-1,0]}(\proj\Lambda)$, which is also a mutation conflation.
Then the Auslander--Reiten conflation~$Y\infl E\defl \susp P$ in~$K^{[-1,0]}(\proj\Lambda)$ is a mutation conflation.
\end{lemma}

@@

(0) Since~$P$ is concentrated in only one degree, it is rigid in~~$K^{[-1,0]}(\proj\Lambda)$ and so is~$\susp P$.
Moreover,~$FY=I$ is~$\tau$-rigid, hence~$Y$ is rigid in~$K^{[-1,0]}(\proj\Lambda)$ by~\cite[Lemma 3.4]{AdachiIyamaReiten}.\pg{Injectives are not necessarily tau-rigid. Need that Lambda is a brick algebra?}

@@

(5) $\Hom{K^b}(\susp P,\susp E)= 0$:
Let~$P\xrightarrow{f} E$ be any morphism.
Since~$P$ is rigid,~$f$ factors through the inflation~$\beta$ in the conflation~$Y\infl E\defl \susp P$, and there is some morphism~$g$ such that~$f=\beta g$.
By the previous lemma, or by (4), the morphism~$g$ factors through~$\alpha$: there is some~$h$ such that~$g= h \alpha$.\pg{What is alpha?}

>>>>

\begin{lemma}\label{lemm::initial meshes}
Let~$\Lambda$ be an Artin algebra whose indecomposable injective modules are~$\tau$-rigid\yann{harmless assumption added}, and let~$P$ be an indecomposable projective~$\Lambda$-module.
%which is a brick.
% Let~$I$ be indecomposable injective with socle~$P/\operatorname{rad}P$, and~$\alpha$ be the composition~$P\to\operatorname{soc} I \to I$.
% Complete the morphism~$\alpha$ to a triangle~$P\to Y\to E\to \susp P$ in~$K^{[-1,0]}(\proj\Lambda)$, where~$Y$ is a minimal projective presentation of~$I$.
% Then~$Y\infl E\defl \susp P$ is an Auslander--Reiten conflation in~$K^{[-1,0]}(\proj\Lambda)$, which is also a mutation conflation.
Then the Auslander--Reiten conflation~$Y\infl E\defl \susp P$ in~$K^{[-1,0]}(\proj\Lambda)$ is a mutation conflation.
\end{lemma}

@@

(0) Since~$P$ is concentrated in only one degree, it is rigid in~~$K^{[-1,0]}(\proj\Lambda)$ and so is~$\susp P$.
Moreover,~$FY=I$ is~$\tau$-rigid, hence~$Y$ is rigid in~$K^{[-1,0]}(\proj\Lambda)$ by~\cite[Lemma 3.4]{AdachiIyamaReiten}.\pg{Injectives are not necessarily tau-rigid. Need that Lambda is a brick algebra?}\yann{You are right, they are $\tau^-$-rigid. Not a problem because we assume all indecomposables to be $\tau$-rigid in our theorem.}

@@

(5) $\Hom{K^b}(\susp P,\susp E)= 0$:
Let~$P\xrightarrow{f} E$ be any morphism.
Since~$P$ is rigid,~$f$ factors through the inflation~$\beta$ in the conflation~$Y\infl E\defl \susp P$, and there is some morphism~$g$ such that~$f=\beta g$.
By the previous lemma, or by (4), the morphism~$g$ factors through~$P \xrightarrow{\alpha} Y$: there is some~$h$ such that~$g= h \alpha$.\pg{What is alpha?}
